A Bayesian approach to uncertainty in word embedding bias estimation

### 2023-12-23 paper/CLsubmission/bayesBiasCL.tex
Adds info on submission dates
Updates bib

\documentclass{clv3}

@@

%\pageonefooter{Action editor: \{action editor name\}. Submission received: DD Month YYYY; revised version received: DD Month YYYY; accepted for publication: DD Month YYYY.}

@@

\begin{itemize}
\item  \citet{DBLP:journals/corr/abs-1811-07253} employ Bayesian methods to estimate uncertainty in NLP tasks,
  but they apply their Bayesian Neural Networks-based method to
  sentiment analysis or named entity recognition, not to bias.

>>>>

% \RequirePackage[2020-02-02]{latexrelease}
\documentclass{clv3}

@@

%\pageonefooter{Action editor: Rico Sennrich. Submission received: 22 June 2023; revised version received: 13 December 2023; accepted for publication: 19 December 2023.}

@@

\begin{itemize}
\item  \citet{xiao2018quantifying} employ Bayesian methods to estimate uncertainty in NLP tasks,
  but they apply their Bayesian Neural Networks-based method to
  sentiment analysis or named entity recognition, not to bias.
